Compositional Certified Resource Bounds\ifshort{\vspace{-.15cm}}{}

### 2014-07-08 paper/main.tex
typo

Another interesting rule is {\sc Q:Call}.  It needs to account for the
changes to the stack caused by the function call, the arguments/return
value passing, and the preservation of local variables.  We can sum up
the main ideas of the rule as follows.
\itemskip
\begin{itemize}
\item The potential in the pre- and postcondition of the function
  specification is equalized to its matching potential in the callee's
  pre- and postcondition.
\itemskipIn
\item
  $\!$The potential of intervals $|\inter x y|$ is preserved
  if $x$ and $y$ are local\iffull{ variables,}{,}
\item
  The unknown potentials after the call (e.g.
  $|\inter x g|$, with $x$ local and $g$ global)
  are set to zero in the postcondition.
\end{itemize}
\itemskip
If $x$ and $y$ are local variables and $f(x,y)$ is
called, {\sc Q:Call} splits the potential of
$|\inter x y|$ in two parts, one part to perform the
computation in the function $f$ and one part to keep for
later use after the function call.  This splitting is
realized by the equations $Q = P {+} S$ and $Q' =
P' {+} S'$.  Arguments in the function precondition
$(\Gamma_f, Q_f)$ are named using a fixed vector $\Vargs$
of names different from all program variables.  This
prevents name conflicts from happening and ensures that
the substitution $[\Vargs/\vec x]$ is meaningful.
Symmetrically, we use the unique name $\Vret$ to represent
the return value in the function's postcondition
$(\Gamma'_f, Q'_f)$.

@@

There are techniques~\cite{Braberman08} that can compute the memory
requirements of object oriented programs with region based garbage
collection.  These systems infer invariants and use external tools
that count the number of integer points in the corresponding polytopes
to obtain bonds.  The described technique can handle loops but not
recursive or composed functions.

>>>>

Another interesting rule is {\sc Q:Call}.  It needs to account for the
changes to the stack caused by the function call, the arguments/return
value passing, and the preservation of local variables.  We can sum up
the main ideas of the rule as follows.
\itemskip
\begin{itemize}
\item The potential in the pre- and postcondition of the function
  specification is equalized to its matching potential in the callee's
  pre- and postcondition.
\itemskipIn
\item
  $\!$The potential of intervals $|\inter x y|$ is preserved
  if $x$ and $y$ are local\iffull{ variables.}{.}
\item
  The unknown potentials after the call (e.g.
  $|\inter x g|$, with $x$ local and $g$ global)
  are set to zero in the postcondition.
\end{itemize}
\itemskip
If $x$ and $y$ are local variables and $f(x,y)$ is
called, {\sc Q:Call} splits the potential of
$|\inter x y|$ in two parts, one part to perform the
computation in the function $f$ and one part to keep for
later use after the function call.  This splitting is
realized by the equations $Q = P {+} S$ and $Q' =
P' {+} S'$.  Arguments in the function precondition
$(\Gamma_f, Q_f)$ are named using a fixed vector $\Vargs$
of names different from all program variables.  This
prevents name conflicts from happening and ensures that
the substitution $[\Vargs/\vec x]$ is meaningful.
Symmetrically, we use the unique name $\Vret$ to represent
the return value in the function's postcondition
$(\Gamma'_f, Q'_f)$.

@@

There are techniques~\cite{Braberman08} that can compute the memory
requirements of object oriented programs with region-based garbage
collection.  These systems infer invariants and use external tools
that count the number of integer points in the corresponding polytopes
to obtain bonds.  The described technique can handle loops but not
recursive or composed functions.
